Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-06-11 Paper/paper.tex
Updated text, and moved images

\begin{abstract}
\textbf{abstract needs to be updated}

@@

With starting parameters for most elements except for La, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e. double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); and data from the electronic structure calculation of the La$_2$ molecule was added.
This stage was carried out while keeping parameters for other interactions unchanged.
The following stage involved further fitting of the La--La parameters, namely those related to the electrostatic interaction (EEM shielding, EEM electronegativity, and EMM hardness), and the La--O parameters by adding to the dataset Mulliken charges and geometrical information obtained from the optimized structures of the La$_2$O$_3$ cluster, three La$_4$O$_6$ clusters, and one La$_6$O$_9$ cluster.
Also, the equations of state corresponding to two solid structures of La$_2$O$_3$ were computed and added.

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{three-La-eos.pdf}
\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
\label{fig:laeos}
\end{figure}

@@

\begin{acknowledgement}
This work has been enabled by the use of computing resources provided by Compute Canada.
\end{acknowledgement}

>>>>

\begin{abstract}
\textbf{abstract needs to be updated to reflect last changes}

@@

With starting parameters for most elements except for Lanthanum, the first stage of the parametrization involved fitting the La--La parameters of the force field to the following: quantum mechanically calculated equations of state corresponding to three solid phases of La, i.e. double hexagonal close packed (dhcp, $\alpha$-La), face centered cubic (fcc, $\gamma$-La), and body centered cubic (bcc, $\beta$-La); and data from the electronic structure calculation of the La$_2$ molecule was added.
This stage was carried out while keeping parameters for other interactions unchanged.
The following stage involved further fitting of the La--La parameters, namely those related to the electrostatic interaction (EEM shielding, EEM electronegativity, and EMM hardness), and the La--O parameters by adding to the dataset Mulliken charges and geometrical information obtained from the optimized structures of the La$_2$O$_3$ cluster, three La$_4$O$_6$ clusters, and one La$_6$O$_9$ cluster.
Also, the equations of state corresponding to two solid structures of La$_2$O$_3$ were computed and added.

@@

@@

\begin{acknowledgement}
This work was supported by the Canada First Research Excellence Fund (CFREF) Global Research Initiative (GRI) in Sustainable Low Carbon Unconventional Resources.
Computational work has been enabled by the use of computing resources provided by Compute Canada.
\end{acknowledgement}

\begin{figure}[hbtp]
\centering
\includegraphics[width=\textwidth]{three-La-eos.pdf}
\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
\label{fig:laeos}
\end{figure}
